---
author: "Gabriel Zanlorenssi"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Presidential Approval - Brazil

Historical approval of Brazilian presidents. 

Source: Datafolha. Complemented with IBOPE data in the first years of Sarney government when IBOPE asked the same question as Datafolha.

Variables:

* presidente: name of president.
* year
* day: last day that respondents were interviewed.
* month: month that respondents were interviewed.
* otimo_bom: percentage that evaluate the government as "ótimo" (very good) and "bom" (good).
* regular: percentage that evaluate the government as "regular".
* ruim: percentage that evaluate the government as "ruim" (bad) or "péssimo" (very bad).
* nsabe: don't know.
* na: missing.
* insitituto: source.
* pergunta: indicates that answers were for the popularity question (with categorical values instead of a binary approval variable yes/no).

Last update: 02/18.

# In R..

## Open dataset

```{r}
aprovacao <- read.csv2("aprovacao.csv")
```

## Generating time variable

```{r, message=F, warning=F}
library(dplyr)

aprovacao <- aprovacao %>% 
  mutate(date = as.Date(paste(day, month, year, sep="/"), format = "%d/%m/%Y"))
```

## Good or very good

```{r, message=F, warning=F}
library(ggplot2)

aprovacao %>% 
  ggplot() +
  geom_line(aes(x = date, y = otimo_bom, col = presidente)) +
  scale_color_manual(values = c("#53868B", "#CD2626", "#0000EE", "#CDAD00", "#EE2C2C", "#8B6508", "#FFC125")) + 
  theme_bw()
```


## Regular

```{r, message=F, warning=F}
library(ggplot2)

aprovacao %>% 
  ggplot() +
  geom_line(aes(x = date, y = regular, col = presidente)) +
  scale_color_manual(values = c("#53868B", "#CD2626", "#0000EE", "#CDAD00", "#EE2C2C", "#8B6508", "#FFC125")) + 
  theme_bw()
```

## Bad or very bad

```{r, message=F, warning=F}
library(ggplot2)

aprovacao %>% 
  ggplot() +
  geom_line(aes(x = date, y = ruim, col = presidente)) +
  scale_color_manual(values = c("#53868B", "#CD2626", "#0000EE", "#CDAD00", "#EE2C2C", "#8B6508", "#FFC125")) + 
  theme_bw()
```

## Score

Using a score:

* Score = good and very good + (regular * 0) - bad and very bad

```{r, message=F, warning=F}
library(ggplot2)

aprovacao %>% 
  mutate(score = otimo_bom - ruim) %>% 
  ggplot() +
  geom_line(aes(x = date, y = score, col = presidente)) +
  scale_color_manual(values = c("#53868B", "#CD2626", "#0000EE", "#CDAD00", "#EE2C2C", "#8B6508", "#FFC125")) + 
  geom_hline(yintercept =  0) + 
  theme_bw()
```

